What is MaxEnt?

### 2015-06-14 ms.tex
minor edits

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $F$ is known, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

In this section we'll look at a different kind of testable information that
relates to $F$, but is not the expected value. What if we receive testable
information about the marginal distribution for $F$?

For any distribution $p(\xx)$, the marginal distribution for $F$ is:
\begin{eqnarray}
p(F) &=& \sum_{\xx}\mathds{1}\left[f(\xx) = F\right]p(\xx)\label{eqn:constraint}
\end{eqnarray}
If $p(F)$ is a specified function, this is a large number of expected
value constraints on $p(\xx)$, one for each element of the hypothesis space
of possible $F$ values.

Therefore the probability distribution
$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
constraint~\ref{eqn:constraint} is:
\begin{eqnarray}
p(\xx) &=& \frac{q(\xx)}{Z}\exp\left\{-\sum_F \lambda_F \mathds{1}
\left[f(\xx) = F\right]  \right\}
\end{eqnarray}

>>>>

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

In this section we'll look at a different kind of testable information that
relates to $F$, but is not the expected value. What if we receive testable
information that asserts the marginal distribution for $F$?
For any distribution $p(\xx)$, the marginal distribution for $F$ is:
\begin{eqnarray}
p(F) &=& \sum_{\xx}\mathds{1}\left[f(\xx) = F\right]p(\xx)\label{eqn:constraint}
\end{eqnarray}
If $p(F)$ is a specified function, this is a large number of expected
value constraints on $p(\xx)$, one for each element of the hypothesis space
of possible $F$ values. Clearly, the specified marginal $p(F)$ cannot assign
non-zero probability to any possible $F$ values that have zero probability
under $q(\xx)$.

Since Equation~\ref{eqn:constraint} is really just a set of expectations,
the probability distribution
$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
constraint~\ref{eqn:constraint} is:
\begin{eqnarray}
p(\xx) &=& \frac{q(\xx)}{Z}\exp\left\{-\sum_F \lambda_F \mathds{1}
\left[f(\xx) = F\right]  \right\}
\end{eqnarray}
